---
title: "anchor"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

# Explore functions

Open this .Rmd file via 'xxx.Rproj' in working directory.

calibrateScale() and calibrate() gives three ways of automating anchor file preparation. 
  - ancShift: shift of anchors kept.
  - ancTest2Read: name of test (xxx: 'xxx_anc.txt' file in 'output' folder).
  - ancDf: dataframe of anchor delta (and step) estimates.
  
Can also prepare anchor file by yourself and put that into 'input' folder. Then,
use default value of NULL for the three arguments above.

## calibrateScale() anchors a list of tests

```{r}
calibrateScale(
  keyDfLst,
  pid,
  n_cov,
  est_type = "wle",
  ancShiftLst = NULL,
  ancTest2ReadLst = NULL,
  ancDfLst = NULL,
  slope = NULL,
  intercept = NULL,
  extrapolation = FALSE
)
```

## calibrate() anchors one test

```{r}
calibrate(
  anchor=TRUE, # can ignore if any of ancShift, ancTest2Read, ancDf is not NULL
  test,
  respDf = NULL,
  keyDf,
  pid,
  n_cov,
  ancShift = NULL,
  ancTest2Read = NULL,
  ancDf = NULL,
  est_type = "wle",
  slope = NULL,
  intercept = NULL,
  extrapolation = FALSE
)  
```
