---
title: "equate"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

# Explore functions

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

## Use dataframe as input

```{r}
Equate(df=df, test='Elana_math', vars=c('NSW', 'VIC'))
# arg 'df': dataframe with cols of 'item','delta.x', error.x','delta.y','error.y'
# .x relates to vars[[1]], .y relates to vars[[2]]
```

Use of functions below assumes that .shw and other files with names associated 
with test/test form/grade are in 'output' folder in working directory.

## Use CQ output (.shw) as input

```{r}
Equate_shw(test='elana_math', vars=c('NSW', 'VIC'))
```

## Horizontal equating

```{r}
Equate_Hrz(test='R', grades=c(2:6), forms=c('A','B'))
# files names should cover all combinations of args 'grades' and 'forms' (e.g., R_2A.shw)
```

## Vertical equating

```{r}
Equate_Vrt(test='R', grades=c(2:10))
# files names should cover all elements of arg 'grades' (e.g., R_2.shw)
```