---
output: bookdown::html_document2
params:
    test: 'test'
    DIFVar: 'Gender'
    vars: c('Girls', 'Boys')
    facil_cut: 10
    output: output
title: DIF Analysis of `r DIFVar` on `r test` Steps
---

```{r setup, include=FALSE}
library(RaschKit)
library(tidyverse)
library(knitr)

knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
options(knitr.table.format = "simple")
```

# Recommendation

`r output[['comments']]$Details`

# Procedures

Table \@ref(tab:steps) shows the steps taken to do the DIF analysis.

```{r steps, echo=FALSE}
output[['step']] %>% 
    knitr::kable(caption = "Steps used to detec DIF parameters")
```

# Shift Method

Table \@ref(tab:shift-stats) shows the shifts of item statistics before and 
after review. It shows that removal of DIF item steps has improved correlation, 
mean shift, and ratio of standard deviation.

```{r shift-stats}
output[['shift']] %>% 
    knitr::kable(caption = "Shifts of statistics before and after review")
```

# Statistics Before Review

Table \@ref(tab:bfr-rvw) shows the item step statistics before review. From the table, 
we can see that `r output[['flag']] %>% filter(flag==1) %>% nrow()` item steps 
show DIF between `r vars[[1]]` and `r vars[[2]]`.

```{r bfr-rvw}
output[['flag']] %>% 
    knitr::kable(caption = "Item statistics before review")
```

# Statistics After Review

Table \@ref(tab:afr-rvw) shows the item step statistics after review. Now, the statistics
satisfy all the criteria.

```{r afr-rvw}
output[['final']] %>% 
    knitr::kable(caption = "Item statistics after review") 
```

# Scatterplot of Step Difficulty Estimates

Figure \@ref(fig:logit-scatter) shows the scatterplots of item step logit difficulty 
estimates between `r vars[[1]]` and `r vars[[2]]` both before (top) and after 
(bottom) review. The caption at bottom right of the scatterplot on top shows 
all the criteria used to detect DIF item steps.

```{r logit-scatter, fig.cap = "Scatterplot of logit difficulty estimates", fig.width=6, fig.height=12}
output[['plot_DIF']]
```

