---
output: bookdown::html_document2
params:
    test: 'test'
    DIFVar: 'nation'
    output: output
title: DIF Analysis of `r toupper(DIFVar)` on `r toupper(test)`
---

```{r setup, include=FALSE}
library(RaschKit)
library(tidyverse)
library(knitr)

knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
options(knitr.table.format = "simple")
```

# Recommendation

Table \@ref(tab:comments) shows the findings from the DIF analysis. At the end 
is the recommendation on how to handle the DIF items.

```{r comments, echo=FALSE}
output[['comments']] %>% 
    knitr::kable(caption = "Findings and recommendation")
```

# Procedures

Table \@ref(tab:steps) shows the steps taken to do the DIF analysis.

```{r steps, echo=FALSE}
output[['step']] %>% 
    knitr::kable(caption = "Steps used to detec DIF parameters")
```

# Statistics with Flags

Table \@ref(tab:bfr-rvw) shows the Bonferroni test results between adjusted 
item deltas estimated within each subgroup of the DIF variable and the item's 
average delta across all categories. Any significance test result has been marked 
with '*' in the 'sig_' column asscociated with each category.

```{r bfr-rvw}
output[['flags']] %>% 
    knitr::kable(caption = "Item statistics with flags")
```

# Statistics Used to Flag Items

Table \@ref(tab:afr-rvw) shows the item statistics used to do the Bonferroni tests. 
This includes item deltas, errors, and standardised difference between 
item deltas estimated within each DIF variable category and all categories' mean. 


```{r afr-rvw}
output[['stats']] %>% 
    knitr::kable(caption = "Item statistics used to flag items") 
```

# Scatterplot of Difficulty Estimates

Figure \@ref(fig:logit-scatter) shows the scatterplots of item logit difficulty 
estimates within each DIF variable category and the mean. 

```{r logit-scatter, fig.cap = "Scatterplot of logit difficulty estimates", fig.width=8, fig.height=12}
output[['plot_DIF']]
```

