---
output: 
  bookdown::html_document2:
    toc: true
    toc_float: 
      collapsed: true
    toc_depth: 3
    number_sections: true
    theme: paper

params:
  test: 'test'
  vars: c('Test1', 'Test2')
  step: FALSE
  DIF: FALSE
  output: output
title: Analysis of `r if (DIF) 'DIF' else 'Equating'` on `r test` Between `r vars[[1]]` and `r vars[[2]]` `r if (step) 'Steps'`
---

```{r setup, include=FALSE}
library(RaschKit)
library(tidyverse)
library(knitr)
library(bookdown)

knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
options(knitr.table.format = "simple")
```

# Recommendation

`r output[['comments']]$Details`

# Procedures

Table \@ref(tab:steps) shows the steps taken to do the 
`r if (DIF) 'DIF' else 'Equating'` analysis.

```{r steps, echo=FALSE}
output[['step']] |> 
  knitr::kable(caption = "Steps used to detec DIF parameters")
```

# Shift Method

Table \@ref(tab:shift-stats) shows the shifts of parameter estimates before and 
after review. It shows that removal of DIF parameters has improved correlation, 
mean shift, and ratio of standard deviation.

```{r shift-stats}
output[['shift']] |> 
  knitr::kable(caption = "Shifts of statistics before and after review")
```

# Statistics Before Review

Table \@ref(tab:bfr-rvw) shows the parameter estimates before review. From the table, 
we can see that `r output[['flag']] |> filter(flag==1) |> nrow()` parameter estimates 
show DIF between `r vars[[1]]` and `r vars[[2]]`.

```{r bfr-rvw}
output[['flag']] |> 
  knitr::kable(caption = "Parameter estimates before review")
```

# Statistics After Review

Table \@ref(tab:afr-rvw) shows the parameter estimates after review. Now, the statistics
satisfy all the criteria.

```{r afr-rvw}
output[['final']] |> 
  knitr::kable(caption = "Parameter estimates after review") 
```

# Scatterplot of Difficulty Estimates

Figure \@ref(fig:logit-scatter) shows the scatterplots of logit difficulty 
estimates between `r vars[[1]]` and `r vars[[2]]` both before (top) and after 
(bottom) review. The caption at bottom right of the scatterplot on top shows 
all the criteria used to detect DIF item steps.

```{r logit-scatter, fig.cap = "Scatterplot of logit difficulty estimates", fig.width=7, fig.height=14}
output[['plot_DIF']]
```

