---
title: "explore data"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()

create_folders()
```

Open this .Rmd file via 'xxx.Rproj' in working directory. Explore data via 
the following functions.

# Check data and codebook

## Data

Read data to be used for 

```{r}
respDf <- haven::read_sav('data/test.sav') # 'respDf' of calibrate()
```

## Codebook

```{r}
keyDf <- readxl::read_xlsx(
    list.files(here::here('dataRaw'), 
    'codebook', # revise to unique string in file name
    full.names = TRUE)
  ) |> 
  select(Item, Key, Max_score) # 'keyDf' of calibrate()
```

## Update key after review

This may occur when you send 1st round of item analysis results to test developers
and they advise psychometricians to change key, use double key, or remove items.

```{r}
keyDf[25, 'Key'] <- 'A'
```

# Explore functions

## Check response categories' frequencies

```{r}
n_cov <- 4 # number of covariates before responses

# put option frequencies into dataframe
optFreq <- freq_resps_cat(
  respDf[(n_cov+1):ncol(respDf)], 
  wide = TRUE, # wide frequency table
  prop = FALSE # TRUE: proportion table
) 
```

Check whether any item has responses other than valid ones. To recode
invalid codes, either use miss_recode() or set them as 'missCode2Conv' argument 
of calibrate(). For option 1, use default 'missCode2Conv=NULL' for calibrate().

## Remove missing columns/rows

If all-missing items (columns) are found, can use missAll_remove_cols() to remove
all-missing columns or missAll_remove_rows() to detect all-missing cases (rows).

```{r}
missAll_remove_cols(
  df
) 
missAll_remove_rows(
  df, 
  begin, 
  end, 
  rm = TRUE # FALSE: only show all-missing flag; keep full data
)
```

## Recode embedded/trailing missing as 'M'/'R'

Do once for each test domain if test has more than one domain.

```{r}
miss_recode(
  df,
  begin, # specify beginning and end of test section
  end,
  code_emd = "M",
  code_trail = "R",
  code_allMiss = NA_character_,
  miss_code = c("@@", "."), # check optFreq for missing codes
  to_dgt = FALSE,
  to_ltr = FALSE
)
```

## Recode disconnected scores in polytomous scoring

If any item has scores recoded, a file named 'xxx_recode_score.csv' will be saved 
in 'data' folder.

```{r}
poly_recode(
  test,
  keyDf, 
  respDf, 
  n_cov, 
  c('r','R','m','M','9','x','X','.','',' ',NA)
)
```

