---
title: "calibrate"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

# Explore function

## calibrateLst() calibrates a list of tests (one test needs be put in list)

```{r}
calibrateLst( # include format, hyperlink, flag color
  respDfLst = NULL, 
  keyDfLst, 
  pid, 
  n_cov,
  run
)
```

## calibrateCon() merges grade response dataframes and codebooks before 
## performing free calibrarion by regressing on grade

```{r}
calibrateCon(test, grdIntVec, cdLst, pid, grdNm, covNmVec)
```

## calibrate() calibrates one test

```{r}
calibrate(
  test,
  respDf = NULL,
  keyDf,
  pid,
  n_cov
)
```

Below are useful arguments of 'calibrate' (one test). 

### Must set 

test: Test name, e.g., 'GAT'; any meaningful name; 'xxx' below.
pid: Candidate ID variable name in data.
n_cov: Number of covariates before responses.
keyDf: 
  - Item: item labels.
  - Key: key for MC items. Use 1 for constructed responses (CR).
  - Max_score: Maximum score for MC (and CR items). 
  - Key2: 2nd key for any item. Can ignore if no double key.

### May ignore

respDf: Ignore if 'xxx.sav' (or xxx.xlsx) is in 'data' folder.

### Set if test developer advises so after review

delVec: int Vector of item order, or char vector of item labels.
dblKeyLst : list(`5`=c(1,3), `29`=c(3,4)).

### Regressor

regrNmVec: categorical vector of regressor names in data.

### Multi-dimensional modeling

nDimVec: integer Vector of dimensions' item numbers in test.
dimNmVec: dimension names (e.g., c('Literacy', 'Numeracy')); any meaningful name.

### Extra lines in CQ control file

section_extr: Vector of strings as CQ command, if needed to add to control file.

### Item flagging criteria

Can change values to satisfy project requirements.

easy, hard, iRst, fit_w, fit_u: For flagging items.
dFallThr, dRiseThr: For comments on CCC's.

## Explore more

Run '?calibrate' etc. for details.
