---
title: "DIF"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

# Explore function

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

## DIFVarTests() perfomrs chi-square tests on dichotomous DIF variable (and steps) and 
## Bonferroni tests on polytomous DIF variable

This comprehensive function applies to a vector of DIF variables contained in a list
of response dataframes (one test needs be put in list).

Summary files named with DIF variables are put in 'DIF' folder. If 'test3term'
is given, DIF analysis on both item and steps are done and summaries are put 
side by side on 'summary' sheet in summary file.

```{r}
DIFVarTests( # include format, hyperlink, flag color
  testVec = NULL,
  respDfLst = NULL,
  difVarLst = NULL,
  n_cov = NULL,
  pid = NULL,
  keyDfLst = NULL,
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_std_cut = 4,
  design_effect = 1,
  resltReady = FALSE, # TURE when ConQuest output files are in 'DIF' folder
  iter = TRUE, # FALSE if to compare with results from using ACER DIF templates
  test3term = NULL # specify if DIF on steps is needed
)
```

For tests that have polytomous items, 
  - test3term=NULL: only ConQuest model 'item-DIFVar+item*DIFVar+item*step;' is run.
    Model results are used for item delta DIF analysis.
  - stest3term=c('xxx', 'xxx'): for tests in 'stest3term', both above model and model with 
    'item-DIFVar+item*DIFVar+item*step*DIFVar;' are run. Results of 1st model 
    are used for item delta DIF analysis, and those of 2nd model for step DIF analysis.

## DIFDimOne() performs significance tests on facet modeling results

Only use this when the polytomous DIF variable is external to test takers. 
Examples are educator and rater.

```{r}
# polytomous DIF variable
DIFDimOne( # include format, hyperlink, flag color
  method = "Facet",
  test,
  pid,
  n_cov,
  DIFVar,
  respDf = NULL,
  filetype = "sav",
  keyDf,
  vars = NULL,
  poly_facet = FALSE,
  n_resp = NULL,
  regrNmVec = NULL,
  quick = TRUE,
  section_extr = NULL,
  prep_process = FALSE,
  save_xlsx = TRUE,
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_std_cut = 4,
  iter = FALSE,
  step = FALSE,
  design_effect = 1,
  pweight = NULL
)
```

## DIFDimMulti() performs DIF analysis on one dichotomous or polytomous variable
## when a test has more than one domain

```{r}
DIFDimMulti(
  method = c("chi_square", "Bonferroni"), # choose one
  test,
  DIFVar,
  pid,
  n_cov,
  nDimVec,
  dimNmVec,
  respDf = NULL,
  filetype = "sav",
  keyDf,
  vars = NULL,
  regrNmVec = NULL,
  quick = TRUE,
  step = FALSE,
  section_extr = NULL,
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_std_cut = 4,
  design_effect = 1,
  scores = NULL,
  prep_process = FALSE,
  pweight = NULL
)
```
