---
title: "equate"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

# Explore functions

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

## equateLst() performs DIF analysis on a list of delta dataframes (one test needs be put in list)

If indDfLst is available, its stats and plots are added to summary file.

```{r}
tests <- c('N', 'R', 'WA')
vars <- c('trial', 'live')
stats <- c('delta', 'ind')

lst <- list()
for (i in 1:2) {
 lst[[i]] <- map2(
    map(
      tests, 
      ~readxl::read_xlsx(
        'equating/stats.xlsx', 
        paste0(.x, '.', stats[[i]], '.', vars[[1]]) #e.g., N.delta.trial
      )
    ),
    map(
      tests,
      ~readxl::read_xlsx(
        'equating/stats.xlsx',
        paste0(.x, '.', stats[[i]], '.', vars[[2]]) #e.g., R.ind.live
      )
    ),
    ~inner_join(.x, .y, by='item')
  )  
}  

equateLst( # include format, hyperlink, flag color
  deltaDfLst=lst[[1]] |> 
    `names<-`(tests),
  vars,
  p_cut = 0.05,
  DIF_cut = c(0.3, 0.3, 0.5), # vector of cuts if tests vary in cut
  DIF_std_cut = c(3.5, 3.5, 40), # vector of cuts if tests vary in cut
  design_effect = 1,
  step = FALSE,
  iter = FALSE,
  indDfLst = lst[[2]], # NULL if no stats on facility, discrimination, infit 
  sigma=FALSE
)
```

Ensure that folders below contain certain file types.
 - 'output': xxx_its.xls, xxx_shw.txt, xxx_shw.xls.
 - 'data': xxx_Labels.txt.
Those files have names associated with test form or grade. 

For horizontal equating (Hrz), files names in 'output' folder should cover 
all combinations of 'linkTypeLst'. For example, if linkTypeLst is 
list(Hrz=list(grades=c(2:3), forms=c('A','B'))), shw.xls-type files should 
include 'xxx_2A_shw.xls', 'xxx_2B_shw.xls', 'xxx_3A_shw.xls', 'xxx_3B_shw.xls'.
 
## equate2Type() does horizontal and vertical equating

```{r}
equate2Type( # include format, hyperlink, flag color
  linkTypeLst=list(
    Hrz=list(
      grades=c(2:10),
      forms=c('A', 'B')
    )
  ), # Vrt: list(Vrt=c(2:10))
  test,
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_std_cut = 4,
  step = FALSE,
  iter = TRUE, 
  sigma=FALSE, 
  run='free_separate'
)
```
