---
title: "equate"
author: "Xiaoliang Zhou"
date: `r format(Sys.time(), "%d %B, %Y")`
output: html_document
---

```{r}
library(RaschKit)
install_packages_ls()
```

# Explore functions

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

## equateLst() performs DIF analysis on a list of delta dataframes (one test needs be put in list)

If indDfLst is available, its stats and plots are added to summary file.

```{r}
equateLst( # include format, hyperlink, flag color
  deltaDfLst,
  vars,
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_adj_cut = 4,
  design_effect = 1,
  step = FALSE,
  iter = TRUE,
  indDfLst = NULL
)
```

Use of functions below assumes that xxx_shw.xls and other files with names associated 
with test form or grade are in 'output' folder in working directory.

## equate2Type() does horizontal and vertical equating

```{r}
equate2Type( # include format, hyperlink, flag color
  type = c("Hrz", "Vrt"),
  test,
  grdIntVec = c(2:10),
  forms = c("A", "B"),
  p_cut = 0.05,
  DIF_cut = 0.5,
  DIF_adj_cut = 4,
  step = FALSE,
  iter = TRUE
)
# files names in 'output' folder should cover all combinations of args
 # - 'grades' and 'forms', e.g., 'R_2A_shw.xls' (horizontal)
 # - 'grades', e.g., 'R_2_shw.xls' (vertical)
```
