---
title: "anchor"
author: "Xiaoliang Zhou"
date: '2022-11-25'
output: html_document
---

# Install software (Refer to 'explore data.Rmd' in 'rCode' foler)

```{r}
library(RaschKit)
install_packages_ls()
create_folders() 
```

# Explore functions

Open this .Rmd file via 'xxx.Rproj' in working directory.
Select function below for different cases. Functions would output instructions 
on where to find report and/or result files.

Prepare key file (Refer to sample Sheet 'test' in anchors.xlsx).
- In anchors.xlsx in 'data' folder, add a sheet with name same as 'test' 
  argument of 'calibrate'. Use codebook to create 
- On the sheet, add columns below.
  - Item: item labels.
  - Delta: anchor estimates.  
- If you're using an .anc file from previous run, copy that file from 'output'
  folder into 'input' folder and set 'anchor_read=TRUE' in Function calibrate. 

Note that anchors' logit difficulty estimates in Column 'Delta' would be used to 
anchor current cycle's items and candidates onto previous cycle/run and 
produce equivalence table and anchored ability estimates.

```{r}
# Set 'anchor' as TRUE to do anchoring
calibrate(anchor=TRUE, test='FPA', pid='pid', n_cov=1, keys=keys, labels=labels)
```