---
title: "explore data"
author: "Xiaoliang Zhou"
date: '2022-06-17'
output: html_document
---

# Install software

Make sure ACER ConQuest has version 5.23.4 on your machine.

Install 'conquestr' 0.9.995 (Check version: packageVersion('conquestr'))
  - Create a project file 'xxx.Rproj' in a working directory.
  - Open 'xxx.Rproj'. From bottom right pane.    
    - click 'Packages' (3rd button after 'Files', 'Plots').
    - click 'Install'. From 'Install from', select 'Package Archive File...'.
    - Click 'Browse'. Enter into 'File name' file path 
      'P:\ACER ConQuest\Admin\InHouse - ConQuest Latest versions\conquestr\old'.
    - Select 'conquestr_0.9.995.zip'. 
    - Click 'Open'. 
    - Click 'Install'.

```{r}
library(RaschKit)
install_packages_ls()
create_folders() 
```

```{r}
# 1. move this .Rmd file into the 'rCode' folder just created.
# 2. Put received files into 'dataRaw' folder.
# 3. Open this .Rmd file via 'xxx.Rproj'.
# 4. Explore data via the following functions.
```

# Recode embedded/trailing missing as 'M'/'R'
# Do once for each test dimension if test has more than one domain

```{r}
miss_recode(df=elena, begin=10, end=40) #specify beginning and end of test section
```

# Remove missing columns/rows

```{r}
missAll_remove_cols(df=data)
# rm=FALSE: all-missing candidates will have 'flag_miss' as 1
missAll_remove_rows(df, begin=10, end=39) 
```

# Check response categories' frequencies

```{r}
n_cov <- 4 # number covariates before response columns ind data
lapply(resp[-c(1:n_cov)], table) 
```

